### 2022-09-14 input/figsimplerproblem.tex
reworked figure and 20p
toward camera ready
working on newpages

\begin{figure*}[t]
  \newcommand{\SCALE}{0.8}

  \newcommand{\SMSG}{\tiny}
  \newcommand{\OACK}{0.5}

@@

  \begin{center}
    \subfloat[Part A][\label{fig:problemA}Both $a$ and $c$ become sources.
      $w_{ab} = 2$; $w_{bc} = 1$.]{\input{input/figsimplerproblemA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:problemB}$a$ and $c$ delete their partition while $b$ delivers and forwards $\alpha_a$.]
             {\input{input/figsimplerproblemB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:problemC}$b$ blocks the only transiting
      $\delta_a$ while $b$ delivers and forwards $\alpha_c$.]
             {\input{input/figsimplerproblemC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:problemD}$a$ receives + delivers $\alpha_c^3$.]
    %$\alpha_c^3$ reaches $a$ that delivers it.]
             {\input{input/figsimplerproblemD.tex}}
    \hspace{5pt}
    \subfloat[Part E][\label{fig:problemE}$a$ receives + delivers $\delta_c$.]
    %$\delta_c$ reaches $a$ that delivers it.]
             {\input{input/figsimplerproblemE.tex}}
    \hspace{5pt}
    \subfloat[Part F][\label{fig:problemF}$c$ is stuck in a stale $P_a$.]%$c$ stays forever in a stale partition: $P_a$.]
             {\input{input/figsimplerproblemF.tex}}
  \end{center}
  \caption{\label{fig:problem}% Even in the simplest scenarios,
    The naive propagation of messages is
    insufficient to guarantee consistent partitioning. If $c$ had
    children, they would stay in the wrong partition too.}
\end{figure*}

>>>>

\begin{figure*}[t]
  \renewcommand{\SCALE}{0.8}

  \newcommand{\SNODE}{\scriptsize}
  \newcommand{\SMSG}{\tiny}
  \newcommand{\OACK}{0.5}

@@

  \begin{center}
    \subfloat[Part A][\label{fig:problemA}Both $a$ and $c$ become sources.
      $w_{ab} = 2$; $w_{bc} = 1$.]{\input{input/figsimplerproblemA.tex}}
    \hspace{2pt}
    \subfloat[Part B][\label{fig:problemB}$a$ and $c$ delete their partition while $b$ delivers and forwards $\alpha_a$.]
             {\input{input/figsimplerproblemB.tex}}
    \hspace{2pt}
    \subfloat[Part C][\label{fig:problemC}$b$ blocks the only transiting
      $\delta_a$ while $b$ delivers and forwards $\alpha_c$.]
             {\input{input/figsimplerproblemC.tex}}
    \hspace{2pt}
    \subfloat[Part D][\label{fig:problemD}$a$ receives, delivers, and forwards $\alpha_c^3$.]
    %$\alpha_c^3$ reaches $a$ that delivers it.]
             {\input{input/figsimplerproblemD.tex}}
    \hspace{2pt}
    \subfloat[Part E][\label{fig:problemE}$a$ receives, delivers, and forwards $\delta_c$.]
    %$\delta_c$ reaches $a$ that delivers it.]
             {\input{input/figsimplerproblemE.tex}}
    \hspace{2pt}
    \subfloat[Part F][\label{fig:problemF}$c$ is stuck in a stale partition $P_a$.]%$c$ stays forever in a stale partition: $P_a$.]
             {\input{input/figsimplerproblemF.tex}}
  \end{center}
  \caption{\label{fig:problem}% Even in the simplest scenarios,
    The naive propagation of messages is
    insufficient to guarantee consistent partitioning. If $c$ had
    children, they would stay in the wrong partition too.}
\end{figure*}

### 2022-09-14 input/proposal.tex
working on newpages

A first step to avoid staying in inconsistent state is to extend the
behavior of each \process so \processes such as $c$, that would remain
in a wrong partition, use their history of receipt and delivery to
detect the possible blocking of staleness notifications that can
hinder reaching consistent partitioning.  In Figure~\ref{fig:problem},
$b$ blocked the staleness notification $\delta_a$ that $c$ needs since
it belongs to a ephemeral partition $P_c$ that $c$ acknowledges to be
stale before $b$ does. Therefore, $c$ can detect the possible blocking
of $\delta_a$ since it acknowledges that its parent $b$ received,
delivered, and forwarded the stale notification $\alpha_c^1$. In other
terms, $c$ acknowledges that between the delivery of $\alpha_c^1$ and
the delivery of $\delta_c$, $b$ blocked any other $\delta$ and
therefore, it could have blocked $\delta_a$.

>>>>

A first step to avoid staying in inconsistent state is to extend the
behavior of each \process so \processes such as $c$, that would remain
in a wrong partition, use their history of receipt and delivery to
detect the possible blocking of staleness notifications that can
hinder reaching consistent partitioning.  In Figure~\ref{fig:problem},
$b$ blocked the staleness notification $\delta_a$ that $c$ needs since
it belongs to a ephemeral partition $P_c$ that $c$ acknowledges to be
stale before $b$ does. Therefore, $c$ can detect the possible blocking
of $\delta_a$ since it acknowledges that its parent $b$ received,
delivered, and forwarded the stale notification $\alpha_c^1$. In other
terms, \Node $c$ acknowledges that between the delivery of
$\alpha_c^1$ and the delivery of $\delta_c$, \Process $b$ blocked all other
$\delta$ messages and therefore, it could have blocked the most
important staleness notification: $\delta_a$.
